---
title: "CALANGO Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CALANGO Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

  <img src="https://github.com/fcampelo/CALANGO/raw/master/inst/images/CALANGO_LOGO.svg" height="150" alt="CALANGO logo. Drawn by Brazilian artist Berze - https://www.facebook.com/berzearte">

Some examples of CALANGO output are available under `docs/articles/results` in the [CALANGO Github repository](https://github.com/fcampelo/CALANGO).  Example 1 relates to the case study "*Homologous regions and biological roles associated with prophage density in pathogenic and free-living _Escherichia coli_*", and Example 2
is the case study *XYZ*, both of which are presented as part of the manuscript _CALANGO: an annotation-based, phylogeny-aware comparative genomics framework for exploring and interpreting complex genotypes and phenotypes_. 

Please navigate to one of the links below to check the examples:

```{r, results="asis", echo=FALSE}
dirs <- dir("../docs/articles/results/")
cat("\n<br/><ul><br/>")
for (i in seq_along(dirs)){
  url <- paste0("results/", dirs[i], "/index.html")
  txt <- gsub("_", "-", dirs[i], fixed = TRUE)
  cat(paste0('\n<li> <a href="', url, '" target="_blank">', txt, "</a></li><br/>"))
}
cat("</ul><br/>")
```

These examples can be independently reproduced by executing running the script below. The input files (which can be used as templates for other studies) will be stored under 

(Note: This has been tested under different versions of Linux-Ubuntu and macOS, but should work equally well under Windows.)


```{r, eval=FALSE}
install.packages("CALANGO")
library(CALANGO)

# Change target.dir to save under a different folder if needed 
target.dir <- "data"
CALANGO::retrieve_data_files(target.dir)

# Get CALANGO input files for the examples
inputfiles <- dir(paste0(target.dir, "/parameters/"), full.names = TRUE)

# Change to increase number of cores. 
ncores <- 2

# run for all example files
for (i in seq_along(inputfiles)){
  cat("\nProcessing example", i, "of", length(inputfiles), "\n")
  defs <- CALANGO::run_CALANGO(inputfiles[i], cores = ncores)
}

```